A White Noise Approach to Evolutionary Ecology

### 2020-04-06 .A White Noise Approach To Evolutionary Ecology/draft.Rmd
ALL of the rigorous proofs are finally complete

where $r\in\mathbb{R}$ is the intrinsic growth rate in the absence of abiotic selection, $a\geq0$ is the strength of stabilizing selection around the phenotypic optimum $\theta\in\mathbb{R}$, $c\geq0$ captures the sensitivity of fitness to intraspecific competition and we have set $\kappa(x,y)=1$. This exemplary fitness function has a few convenient properties that we breifly take note of. First, the effect of competition induces a local carrying capacity on the population, leading to a finite equilibrium abundance over bounded subsets of $\mathbb{R}$. Second, abiotic selection prevents the abundance density from diffusing too far from the abiotic optimum, leading to a finite equilibrial abundance across all of $\mathbb{R}$, $\lim_{t\to\infty}N(t)=\tfrac{1}{c}(r-\tfrac{1}{2}\sqrt{a\mu})$, finite equilibrial mean trait $\lim_{t\to\infty}\bar x(t)=\theta$ and finite equilibrial phenotypic variance $\lim_{t\to\infty}\sigma^2(t)=\sqrt{\mu/a}$, so long as $|\bar x(0)|<+\infty$, $\sigma^2(0),N(0)>0$ and $r\geq\sqrt{a\mu}/2$. We prove these statements in SM \S\ref{equilib}. By replacing $\kappa(x,y)=1$ with a particular Gaussian function, we will find in \S\ref{coev} and SM \S\ref{diffuse} this fitness function becomes equivalent to a fitness function derived from niche theory that we use to model coevolution driven by resource competition.

>>>>

where $r\in\mathbb{R}$ is the intrinsic growth rate in the absence of abiotic selection, $a>0$ is the strength of stabilizing selection around the phenotypic optimum $\theta\in\mathbb{R}$, $c>0$ captures the sensitivity of fitness to intraspecific competition and we have set $\kappa(x,y)=1$. This exemplary fitness function has a few convenient properties that we breifly take note of. First, the effect of competition induces a local carrying capacity on the population, leading to a finite equilibrium abundance over bounded subsets of $\mathbb{R}$. Second, abiotic selection prevents the abundance density from diffusing too far from the abiotic optimum, leading to a finite equilibrial abundance across all of $\mathbb{R}$, $\lim_{t\to\infty}N(t)=\tfrac{1}{c}(r-\tfrac{1}{2}\sqrt{a\mu})$, finite equilibrial mean trait $\lim_{t\to\infty}\bar x(t)=\theta$ and finite equilibrial phenotypic variance $\lim_{t\to\infty}\sigma^2(t)=\sqrt{\mu/a}$, so long as $|\bar x(0)|<+\infty$, $\sigma^2(0),N(0)>0$ and $r\geq\sqrt{a\mu}/2$. We prove these statements in SM \S\ref{equilib}. By replacing $\kappa(x,y)=1$ with a particular Gaussian function, we will find in \S\ref{coev} and SM \S\ref{diffuse} this fitness function becomes equivalent to a fitness function derived from niche theory that we use to model coevolution driven by resource competition.
